### 2021-11-20 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@393d0d8dc23e3dcd71818a02ea09831f5881e763 🚀

%
\href{https://orcid.org/0000-0002-6506-6487}{Michael D.\,Catchen}%
%
\,\textsuperscript{1,2}\quad %
\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
%
\,\textsuperscript{3,4,2}\quad %
Paul\,CaraDonna%
%
\,\textsuperscript{5,6}\quad %
\href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
%
\,\textsuperscript{1,2}\quad %
\href{https://orcid.org/0000-0002-6248-3007}{Philippe\,Desjardins-Proulx}%
%
\,\textsuperscript{3,2}\quad %
\href{https://orcid.org/0000-0001-9019-0108}{Norma R.\,Forero-Muñoz}%
%
\,\textsuperscript{3,2}\quad %
\href{https://orcid.org/0000-0001-6075-8081}{Andrew\,Gonzalez}%
%
\,\textsuperscript{1,2}\quad %
\href{https://orcid.org/0000-0002-4498-7076}{Dominique\,Gravel}%
%
\,\textsuperscript{4,2}\quad %
Jane E.\,Ogilvie%
%
\,\textsuperscript{5}\quad %
\href{https://orcid.org/0000-0002-6004-4027}{Laura\,Pollock}%
%
\,\textsuperscript{1,2}\quad %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{3,2}\quad %
\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
%
\,\textsuperscript{3,2}\quad %
Julian\,Resasco%
%
\,\textsuperscript{7}

\textsuperscript{1}\,McGill University\quad \textsuperscript{2}\,Québec
Centre for Biodiversity Sciences\quad \textsuperscript{3}\,Université de
Montréal\quad \textsuperscript{4}\,Université de
Sherbrooke\quad \textsuperscript{5}\,Rocky Mountain Biological
Laboratory\quad \textsuperscript{6}\,Chicago Bontanic
Garden\quad \textsuperscript{7}\,University of Colorado Boulder

@@

Species vary in spacem but also

@@

>>>>

%
\href{https://orcid.org/0000-0002-6506-6487}{Michael D.\,Catchen}%
%
\,\textsuperscript{1,2}\quad %
Paul\,CaraDonna%
%
\,\textsuperscript{3,4}\quad %
Jane E.\,Ogilvie%
%
\,\textsuperscript{3}\quad %
\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
%
\,\textsuperscript{5,6,2}\quad %
\href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
%
\,\textsuperscript{1,2}\quad %
\href{https://orcid.org/0000-0002-6248-3007}{Philippe\,Desjardins-Proulx}%
%
\,\textsuperscript{5,2}\quad %
\href{https://orcid.org/0000-0001-9019-0108}{Norma R.\,Forero-Muñoz}%
%
\,\textsuperscript{5,2}\quad %
\href{https://orcid.org/0000-0001-6075-8081}{Andrew\,Gonzalez}%
%
\,\textsuperscript{1,2}\quad %
\href{https://orcid.org/0000-0002-4498-7076}{Dominique\,Gravel}%
%
\,\textsuperscript{6,2}\quad %
\href{https://orcid.org/0000-0002-6004-4027}{Laura\,Pollock}%
%
\,\textsuperscript{1,2}\quad %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{5,2}\quad %
\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
%
\,\textsuperscript{5,2}\quad %
Julian\,Resasco%
%
\,\textsuperscript{7}

\textsuperscript{1}\,McGill University\quad \textsuperscript{2}\,Québec
Centre for Biodiversity Sciences\quad \textsuperscript{3}\,Rocky
Mountain Biological Laboratory\quad \textsuperscript{4}\,Chicago
Bontanic Garden\quad \textsuperscript{5}\,Université de
Montréal\quad \textsuperscript{6}\,Université de
Sherbrooke\quad \textsuperscript{7}\,University of Colorado Boulder

@@

Main idea here: we have interaction information for some subset of the
species pool, and good SDMs for a different subset of the species pool.
There is some overlap in these species poolsHow do we combine this to
predict: species interactions, uncertainty in interactions (which as
increases indicates better use of sampling time).

@@

This predictive model should not be used as definitive prediction:
instead it reveals gaps in our sampling (where we have little confidence
in predictions---see uncertainty figure). Iterative forecasting
(\textbf{Diteze?}): use this model to guide sampling in the future to
validate and update the model, etc.

### 2021-11-20 preprint.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@393d0d8dc23e3dcd71818a02ea09831f5881e763 🚀

\medskip
\begin{flushleft}
{\small
%
\href{https://orcid.org/0000-0002-6506-6487}{Michael D.\,Catchen}%
%
\,\textsuperscript{1,2}, %
\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
%
\,\textsuperscript{3,4,2}, %
Paul\,CaraDonna%
%
\,\textsuperscript{5,6}, %
\href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
%
\,\textsuperscript{1,2}, %
\href{https://orcid.org/0000-0002-6248-3007}{Philippe\,Desjardins-Proulx}%
%
\,\textsuperscript{3,2}, %
\href{https://orcid.org/0000-0001-9019-0108}{Norma R.\,Forero-Muñoz}%
%
\,\textsuperscript{3,2}, %
\href{https://orcid.org/0000-0001-6075-8081}{Andrew\,Gonzalez}%
%
\,\textsuperscript{1,2}, %
\href{https://orcid.org/0000-0002-4498-7076}{Dominique\,Gravel}%
%
\,\textsuperscript{4,2}, %
Jane E.\,Ogilvie%
%
\,\textsuperscript{5}, %
\href{https://orcid.org/0000-0002-6004-4027}{Laura\,Pollock}%
%
\,\textsuperscript{1,2}, %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{3,2}, %
\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
%
\,\textsuperscript{3,2}, %
Julian\,Resasco%
%
\,\textsuperscript{7}
\vskip 1em
\textsuperscript{1}\,McGill University; \textsuperscript{2}\,Québec
Centre for Biodiversity Sciences; \textsuperscript{3}\,Université de
Montréal; \textsuperscript{4}\,Université de
Sherbrooke; \textsuperscript{5}\,Rocky Mountain Biological
Laboratory; \textsuperscript{6}\,Chicago Bontanic
Garden; \textsuperscript{7}\,University of Colorado Boulder\\
\vskip 1em
\textbf{Correspondance to:}\\
Michael D. Catchen --- \texttt{michael.catchen@mail.mcgill.ca}\\
}
\end{flushleft}

>>>>

\medskip
\begin{flushleft}
{\small
%
\href{https://orcid.org/0000-0002-6506-6487}{Michael D.\,Catchen}%
%
\,\textsuperscript{1,2}, %
Paul\,CaraDonna%
%
\,\textsuperscript{3,4}, %
Jane E.\,Ogilvie%
%
\,\textsuperscript{3}, %
\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
%
\,\textsuperscript{5,6,2}, %
\href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
%
\,\textsuperscript{1,2}, %
\href{https://orcid.org/0000-0002-6248-3007}{Philippe\,Desjardins-Proulx}%
%
\,\textsuperscript{5,2}, %
\href{https://orcid.org/0000-0001-9019-0108}{Norma R.\,Forero-Muñoz}%
%
\,\textsuperscript{5,2}, %
\href{https://orcid.org/0000-0001-6075-8081}{Andrew\,Gonzalez}%
%
\,\textsuperscript{1,2}, %
\href{https://orcid.org/0000-0002-4498-7076}{Dominique\,Gravel}%
%
\,\textsuperscript{6,2}, %
\href{https://orcid.org/0000-0002-6004-4027}{Laura\,Pollock}%
%
\,\textsuperscript{1,2}, %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{5,2}, %
\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
%
\,\textsuperscript{5,2}, %
Julian\,Resasco%
%
\,\textsuperscript{7}
\vskip 1em
\textsuperscript{1}\,McGill University; \textsuperscript{2}\,Québec
Centre for Biodiversity Sciences; \textsuperscript{3}\,Rocky Mountain
Biological Laboratory; \textsuperscript{4}\,Chicago Bontanic
Garden; \textsuperscript{5}\,Université de
Montréal; \textsuperscript{6}\,Université de
Sherbrooke; \textsuperscript{7}\,University of Colorado Boulder\\
\vskip 1em
\textbf{Correspondance to:}\\
Michael D. Catchen --- \texttt{michael.catchen@mail.mcgill.ca}\\
}
\end{flushleft}
